---
title: "Untitled"
output: html_document
---
```{r setup, include=FALSE}
install.packages("knitr")
install.packages("dplyr")
install.packages("ggplot2")
install.packages("mgcv")
install.packages("tidyverse")
library(knitr)
library(dplyr)
library(ggplot2)
library(mgcv)
library(tidyverse)
# General set-up for the report.
# I find this useful, but you may improve upon, ignore, or remove
#  (possibly at your own peril).
# Tasks accomplished:
# Don't print out code
# Save results so that code blocks aren't re-run unless code
# changes (cache), _or_ a relevant earlier code block changed (autodep),
# don't clutter R output with messages or warnings (message, warning)
library(MASS)
library(knitr)
opts_chunk$set(echo=FALSE,
               cache=TRUE, autodep=TRUE,
               message=FALSE, warning=FALSE)
# Turn off meaningless clutter in summary() output
options(show.signif.stars=FALSE)
library(ggplot2)
library(mgcv)
```

```{r load-data}
navc <- read.csv("navc.csv")
navc <- na.omit(navc)
```


===============
#Introduction
===============
Description of Datasets, there is only one datasets in our project "navc"
The dataset "navc.csv" has 12 variables and 267(ignoring NA values in the row), which is gathered by the political scientist who studied the question whether the non-violent movements are more or less likely to be effective than violent political movement. The specific question is that is the non-violent political movement have lower probability to achieve their goal compared to the dangerous and threatening political movement.
```{R}
names(navc) <- c("Campaign","Country","Year","Outcome","Nonviol","Democray","Sanctions","Aid","Support","Viol.Repress","Defect","Duration")
Descriptions <- c(
  "The name of the campaign", 
  "The country where the movement happened",
  "The tipping point of movement's activity(year)",
  "The degree of movement's success('failed 0.0','partial success 0.5','fully success 1.0')", 
  "1 for non-violent and 0 for otherwise)", 
  "Quantitive measure of how democratic a nation is from -10(un-democratic) to 10(democratic)", 
  "1 for under international sanctions and 0 otherwise", 
  "1 for foreign government support to domestic government and 0 otherwise",
  "1 for foreign government support to domestic movement and 0 otherwise",
  "1 for governmental violence suppresion and 0 otherwise",
  "1 for big portions of security force by government sided with movement and 0 otherwise",
  "Duration of the campaign")
# Typing the variables:
Type <- c("Categorical",
          "Categorical",
          "Discrete",
          "Continuous",
          "Discrete",
          "Discrete",
          "Discrete",
          "Discrete",
          "Discrete",
          "Discrete",
          "Discrete",
          "Discrete")
# Binding the decriptions to the variables
var.table1 <- cbind(names(navc),Descriptions,Type)
colnames(var.table1)<- c("Variable","Descriptions","Type")
kable(var.table1)
```




```{r cv-function,  include=FALSE }
# Code for cross-validated classification error rates
# From Lecture 12
cv.mdl <- function(data, formulae, fit.function = lm, family=gaussian, nfolds = 5) {
  data <- na.omit(data)
  formulae <- sapply(formulae, as.formula)
  responses <- sapply(formulae, function(form) all.vars(form)[1])
  names(responses) <- as.character(formulae)
  n <- nrow(data)
  fold.labels <- sample(rep(1:nfolds, length.out = n))
  mses <- matrix(NA, nrow = nfolds, ncol = length(formulae))
  colnames <- as.character(formulae)
  for (fold in 1:nfolds) {
    test.rows <- which(fold.labels == fold)
    train <- data[-test.rows, ]
    test <- data[test.rows, ]
    for (form in 1:length(formulae)) {
      current.model <- fit.function(formula = formulae[[form]], data = train, 
                                    family=family) #change here
      predictions <- predict(current.model, newdata = test, type='response') # change here
      test.responses <- test[, responses[form]]
      test.errors <- test.responses - predictions
      mses[fold, form] <- mean(test.errors^2)
    }
  }
  return(colMeans(mses))
}
```



```{r calibration-plot-function, include=FALSE}
# Code from Lecture 12
binary_calibration_plot <- function(y, model, breaks = 0:10/10, 
                                    point.color='blue', line.color='red') {
  fitted.probs = predict(model, type="response")
  ind = cut(fitted.probs, breaks)
  freq = tapply(y, ind, mean)
  ave.prob = tapply(fitted.probs, ind, mean)
  se = sqrt(ave.prob*(1-ave.prob)/table(ind))
  df = data.frame(freq, ave.prob, se)
  g <- ggplot(df, aes(ave.prob,freq)) + geom_point(color=point.color) + 
    geom_abline(slope = 1, intercept = 0,color=line.color) +
    ylab("observed frequency") + xlab("average predicted probability") +
    geom_errorbar(ymin=ave.prob-1.96*se, ymax=ave.prob+1.96*se) +
    ylim(0,1)+xlim(0,1) + 
    geom_rug(aes(x=fitted.probs,y=fitted.probs),data.frame(fitted.probs),sides='b')
  return(g)  
}

```
