---
title: "Untitled"
output: html_document

---
```{r setup, include=FALSE}
# install.packages("knitr")
# install.packages("dplyr")
# install.packages("ggplot2")
# install.packages("mgcv")
# install.packages("tidyverse")
# install.packages("stargazer")
library(knitr)
library(dplyr)
library(ggplot2)
library(mgcv)
library(tidyverse)
library(stargazer)
# General set-up for the report.
# I find this useful, but you may improve upon, ignore, or remove
#  (possibly at your own peril).
# Tasks accomplished:
# Don't print out code
# Save results so that code blocks aren't re-run unless code
# changes (cache), _or_ a relevant earlier code block changed (autodep),
# don't clutter R output with messages or warnings (message, warning)
library(MASS)
library(knitr)
opts_chunk$set(echo=FALSE,
               cache=TRUE, autodep=TRUE,
               message=FALSE, warning=FALSE)
# Turn off meaningless clutter in summary() output
options(show.signif.stars=FALSE)
library(ggplot2)
library(mgcv)
```

```{r load-data}
navc <- read.csv("navc.csv")
cv.glm = function(glmObj) mean((residuals(glmObj) / (1 - hatvalues(glmObj)))^2) 
cv.gam = function(gamObj) mean((residuals(gamObj) / (1 - gamObj$hat))^2) 
```


===============
#Introduction
===============



Description of Datasets, there is only one datasets in our project "navc"
The dataset "navc.csv" has 12 variables and 267(ignoring NA values in the row), which is gathered by the political scientist who studied the question whether the non-violent movements are more or less likely to be effective than violent political movement. The specific question is that is the non-violent political movement have lower probability to achieve their goal compared to the dangerous and threatening political movement.
```{R}
names(navc) <- c("Campaign","Country","Year","Outcome","Nonviol","Democray","Sanctions","Aid","Support","Viol.Repress","Defect","Duration")
Descriptions <- c(
  "The name of the campaign", 
  "The country where the movement happened",
  "The tipping point of movement's activity(year)",
  "The degree of movement's success('failed 0.0','partial success 0.5','fully success 1.0')", 
  "1 for non-violent and 0 for otherwise)", 
  "Quantitive measure of how democratic a nation is from -10(un-democratic) to 10(democratic)", 
  "1 for under international sanctions and 0 otherwise", 
  "1 for foreign government support to domestic government and 0 otherwise",
  "1 for foreign government support to domestic movement and 0 otherwise",
  "1 for governmental violence suppresion and 0 otherwise",
  "1 for big portions of security force by government sided with movement and 0 otherwise",
  "Duration of the campaign")
# Typing the variables:
Type <- c("Categorical",
          "Categorical",
          "Discrete",
          "Continuous",
          "Discrete",
          "Discrete",
          "Discrete",
          "Discrete",
          "Discrete",
          "Discrete",
          "Discrete",
          "Discrete")
# Binding the decriptions to the variables
var.table1 <- cbind(names(navc),Descriptions,Type)
colnames(var.table1)<- c("Variable","Descriptions","Type")
kable(var.table1)
```

=================
#analytical issues
=================


A lot of people always make a assumption that violent movement can be more likely to be successful to achieve their goal than the non-violent movement. But we can see some non violent campaign also can achieve their goal if you take a look at the history of global campaign happened in some countries. In this report, we will use "Bar chart","Logistic regression model","generalized linear model","generalized additive model","**TODO**","**TODO**" to present you about the description of this situation and explain some other related question that can help you understand the analytical question presented below. This dataset is is gathered by the political scientist who studied the question whether the non-violent movements are more or less likely to be effective than violent political movement. The analytic question is that is the non-violent political movement have lower probability to achieve their goal compared to the dangerous and threatening political movement.

For the first question that are non-violent movements more likely to be successful than violent ones? From **Table 1**, we can see the biggest number representing the frequency of violent movement who totally failed during that time compared to the lowest frequency representing the frequency of non-violent movement who totally failed. These two statistics gives people a hint that frequency of violent movement failed is higher than the frequency of non-violent movement failed. Moving to the partially successful movement column, we can see that percentage(51.9%) of violent movement is bigger than that(48.1%) of non-violent for just a bit of amount, I will say that we are not sure about **what the 2 more number can explain something more effective here, we can wait until we do the more advanced model to check that because maybe the two more number does matter when involving other factor**. For the last column, non-violent movement fianlly exceed the violent movement for a little amount as well. **We still need to wait until the advanced model can tell you what the small difference can tell something**. Notice here that If we attribute the partial success to the fully success, the frequency of fully success for both violent and non-violent movement is the same, we cannot see whether violent can contribute to success more likely than non-violent. It is interesting.





=================
#1.are non-violent movements more likely to be successful than violent ones?
=================


```{r, echo=FALSE,fig.cap="**Figure 1.0** _From this picture, non-violent movement tend to have higher frequency of outcome compared to violent movement which is less than that of non-violent movement for just a little bit of amount. We need more advanced model to determine whether non-violent movement will increase the probability of Outcome_"}
vio.fal <- nrow(filter(navc, Outcome == 0.0 & Nonviol == 0.0))
vio.par <- nrow(filter(navc, Outcome == 0.5 & Nonviol == 0.0))
vio.ful <- nrow(filter(navc, Outcome == 1.0 & Nonviol == 0.0))
non.fal <- nrow(filter(navc, Outcome == 0.0 & Nonviol == 1.0))
non.par <- nrow(filter(navc, Outcome == 0.5 & Nonviol == 1.0))
non.ful <- nrow(filter(navc, Outcome == 1.0 & Nonviol == 1.0))
vio.effect <- matrix(c("134  (85.4%)","28  (51.9%)","55  (49.1%)",
                   "23  (14.6%)","26  (48.1%)","57  (50.9%)"), ncol=3,byrow=TRUE)
colnames(vio.effect) <- c("Totally failed","partially successful","fully successful")
rownames(vio.effect) <- c("Violent movement","Non-Violent movement")
kable(vio.effect,caption = "**Table 1.**  Table shows the distribution that frequency of violent or non-violent vs the 3 different degree of success. And the percentage of two types of movement within certain group")
#========
vio.effect <- matrix(c(vio.fal,vio.par,vio.ful,
                   non.fal,non.par,non.ful), ncol=3,byrow=TRUE)
colnames(vio.effect) <- c("Totally failed","partially successful","fully successful")
rownames(vio.effect) <- c("Violent movement","Non-Violent movement")
effect.table <- as.table(vio.effect)
#===============================================================================
vio.effect <- as.data.frame(effect.table)
vio.effect$Var1 <- c("failed","failed","partial_suc","partial_suc","fully_suc","fully_suc")
# Basic Barplot
my_bar=barplot(vio.effect$Freq , border=F , names.arg=vio.effect$Var1 , las=2 , col=c(rgb(0.3,0.1,0.4,0.6) , rgb(0.3,0.5,0.4,0.6)) , ylim=c(0,max(vio.effect$Freq)+20) , main="" )
abline(v=c(2.5 , 4.9) , col="grey")
 
# Add the text 
text(my_bar, vio.effect$Freq+5 , paste("n = ",vio.effect$Freq,sep="") ,cex=1) 
 
#Legende
legend("topright", legend = c("Violent movement","Non-violent movement" ) , 
     col = c(rgb(0.3,0.1,0.4,0.6) , rgb(0.3,0.5,0.4,0.6)) , 
     bty = "n", pch=20 , pt.cex = 2, cex = 0.8, horiz = FALSE, inset = c(0.05, 0.05))

```

-
-
-

But how do we justfiy explicitly the relationship between the outcome and non-violent movement, I introduce the logistic model, which is a subset of the generalized linear regression model. This model can predict the probability that Y belongs to particular category when Y response is discrete and has only two value(EX: 0 or 1). And this model's parameter can take either discrete or continuous variable to predict the probability of response Y. There are two model(), which is the same. For the second formula, it is pretty much like transformation on Y. Here are they:


$$p(X) = \frac {e^{\beta_{0} + \beta_{1}X_{1} + ... + \beta_{p}X_{p}}}{1 + e^{\beta_{0} + \beta_{1}X_{1} + ... + \beta_{p}X_{p}}}$$.


$$log\left( \frac {p(X)}{1-p(X)} \right) = \beta_{0} + \beta_{1}X_{1} + ... + \beta_{p}X_{p}$$

So, after we run the logistic linear regression on variable Nonviol as a predictor and Outcome as a repsonse. we got beta0 and beta1, which you can plug in the formula that I gave to calculate the estimated the probability of The outcome. If the probability of outcome response is greater than one half, we traditionally assign that outcome to 1, and if the proability is less than one half, we traditionally assign that outcome to 0. We do not consider a situation that the probability is exactly one half because it is really rare.


```{R, echo=FALSE}
navc.outcome <- navc
navc.outcome[navc.outcome == 0.5] <- 1.0
glm.outvio <- glm(Outcome ~ Nonviol, data = navc.outcome, family = "binomial")
kable(summary(glm.outvio)$coefficients ,caption = "**Table 2.** _For the_ **Outcome** _data, estimated coefficients of the logistic regression model that predict the probability of_ **Outcome** _using Non-violent movement. Non violent movement is encoded as a dummy variable, with a value of 1 for non violent movement and a value of 0 for a violent movement, and represented by the variable Nonviol i the table_")
```




$$Pr(outcome = 1 |nonviol = 1) = \frac {e^{-0.4789 + 1.7623 *1}}{1+e^{-0.4789 + 1.7623 *1}} = 0.783028 $$
$$Pr(outcome = 1 |nonviol = 0) = \frac {e^{-0.4789 + 1.7623 *0}}{1+e^{-0.4789 + 1.7623 *0}} = 0.382512 $$
In _Table 2_,the coefficient associated with the dummy variable is positive, and the associated p-value is statistically significant**(USING BOOTSTRAP OR SIMULATION PROCEDURES TO TEST COEFFICIENT WHETHER IT CAN BE TRUSTED)**. This indicates that non-violent movement tend to have higher outcome probabilities than violent movement. At this time, the coefficient is hard to interpret**Asking professor if it is ok to interpret the coefficient** because it is not linear anymore. If you have a continuous variable as a predictor, you can calculate the estimated probability and plot them to see the pattern, **which will be shown below for another analysis.**. But this is just for generalized linear model. What if I use generalied additive model on this?

The generalized additive model looks like the following:
$$log\left( \frac {p(X)}{1-p(X)} \right) = \beta_{0} + f(x_{1}) + f(x_{2})... + f(x_{p})$$

```{r,result="asis",echo=FALSE,fig.cap="**Figure  1.1**"}
gam.outvio <- gam(Outcome ~ Nonviol , data = navc.outcome, family = 'binomial')
pred.gam.outvio <- predict(gam.outvio, type='response')
gam.data.frame.outvio <- as.data.frame(matrix(c(pred.gam.outvio,navc.outcome$Nonviol),ncol = 2, byrow = FALSE))
#ggplot(gam.data.frame, aes(factor(V2), V1, color = factor(V2)))+ geom_boxplot()    #to be deleted
table.outvio<- matrix(c(mean(subset(gam.data.frame.outvio, V2 == 0)$V1),mean(subset(gam.data.frame.outvio, V2 == 1)$V1),cv.gam(gam.outvio),
                  .382512,0.783028,cv.glm(glm.outvio)),ncol = 3, byrow = TRUE)
rownames(table.outvio) <- c("Generalized additive model","Generalized linear model")
colnames(table.outvio) <- c("violent movement","non-violent movement","Cross-validation")
table.outvio <- as.data.frame(table.outvio)
kable(table.outvio, caption = "**Table 3.** _This table shows that generalized linear model produces almost exactly the same as the generalized additive model if we have precision 4 th digits. More importantly, the cross validation for two different models is the same, indicating they are both good model for estimating the probability of outcome given whether movement is violent or not_")
# (confusion.gam <- table(navc.outcome$Outcome, as.integer(pred.gam > 0.5),   #to be deleted unless useful
#                         dnn = c('reality','prediction'))) 
#stargazer(table, type = "html", title = "Table with stargazer")   # to be added
```

-



-



-




What if we add another predictor which is the violent repression by government, Is there a difference in this effect between non-violent and violent movement? Let's go check it out!


```{R}
glm.outviorep <- glm(data = navc.outcome, Outcome ~ Nonviol + Viol.Repress, family = 'binomial')
gam.outviorep <- gam(data = navc.outcome, Outcome ~ factor(Nonviol) + factor(Viol.Repress), family = 'binomial')
kable(summary(glm.outviorep)$coefficients, caption = "**Table 4.** _This is coefficient table for the generalized linear model for multiple predictor. We follow the_ **Table 2** _by adding the statement that violence repression by government is encoded as a dummy variable, with a value of 1 for violence repression by government and a value of 0 for not violence repression by government_")
#============================================

pred.gam.outviorep <- predict(gam.outviorep, type='response')
gam.data.frame <- as.data.frame(matrix(c(pred.gam.outviorep,navc.outcome$Nonviol,navc.outcome$Viol.Repress),ncol = 3, byrow = FALSE))

table.outviorep <- matrix(c(0.7640984,mean(subset(gam.data.frame, V2 == 1 & V3 == 1)$V1),
                            0.8596018,mean(subset(gam.data.frame, V2 == 1 & V3 == 0)$V1),
                            0.3702582,mean(subset(gam.data.frame, V2 == 0 & V3 == 1)$V1),
                            0.5263743,mean(subset(gam.data.frame, V2 == 0 & V3 == 0)$V1),
                            cv.glm(glm.outviorep),cv.gam(gam.outviorep)),ncol = 2, byrow = TRUE)
rownames(table.outviorep) <- c("non-violent movement with repression",
                     "non-violent movement without repression",
                     "violent movement with repression",
                     "violent movement without repression",
                     "Cross-validation")
colnames(table.outviorep) <- c("Generalized linear model","Generalized additive model")
table.outviorep <- as.data.frame(table.outviorep)
#cv.mdl(glm.outviorep)
```



From _Table 4_, we notice that the coefficient for nonviol does not change a lot compared to the previous model, it only decrease 0.055. **p-value for nonviol(boostrap)... coefficient for viol.repress... p-value for viol.repress(bootstrap)...(CV.MDL ASKING PROFESSOR)**





```{R}
kable(table.outviorep, caption = "**Table 5.** This table represent that estimated probability of outcome given four different combination of condition on violence(or non-) for movement and violence(or non-) by government under two different model. Cross-validation is given at the bottom of the table under two different model as well")
```

As we can see from _Table 5_, [two different model produce almost the same probability based on two predictor.]. Let's interpreting the frequency in the _Table 5_. As we can see that when government use violent repression to the campaign, non-violent movement has probability .7641, which is much larger than probability 0.3703 violent movement. In other word, when government _is_ using violence repression, non-violent movement tend to be more effective than violent movement. Similarly, when the government did not use the violence repression to movement, non-violent movement produce the probability .8596, which is much larger than the probability of violent movement In other word, when government _isn't_ using violence repression, non-violent movement tend to be more effective to achieve their goal than the violent movement. If regardless of violent or non-violent movement, the probability of outcome will decrease by 0.1 for non-violent movement and by 0.16 for violent movement if government change non-violent repression to violent repression. In other words, if government choose to use violent repression to the movement, movement is less likely to achieve their goal regardless of violent or non-violent movement. We do not compare 0.1 and 0.16 here cause it does not give a lot of information about the effectiveness of violent or non violent.

-





-




-


When we finish looking at the generalized linear model with two predictor on nonviol and viol.repress, let see what if I delete the nonviol predictor, and only looking at the impact violent repression by the government make on the outcome. That is, we will find the probability of outcome given violent repression by the govenment regardless of whether movements are violent or non-violent.


```{r}
glm.outrep <- glm(data = navc.outcome, Outcome ~ Viol.Repress, family = 'binomial')
gam.outrep <- gam(data = navc.outcome, Outcome ~ factor(Viol.Repress), family = 'binomial')
```

=================
#2.Does violent repression by the government make movements more or less likely to be successful
=================

repress vs Outcome
=================
#3.Is there a difference in this effect between movements which are themselves violent and non-violent?
=================




=================
#4.What is the effect of foreign aid to the government and to the movement?
=================




=================
#5.Do non-violent movements become more likely to succeed as the goverment becomes more demoratic?
=================




=================
#6.Does the difference in probability of success between violent and non-violent movements vary with how democratic the government is?
=================

```{r cv-function,  include=FALSE }
# Code for cross-validated classification error rates
# From Lecture 12
cv.mdl <- function(data, formulae, fit.function = lm, family=gaussian, nfolds = 5) {
  data <- na.omit(data)
  formulae <- sapply(formulae, as.formula)
  responses <- sapply(formulae, function(form) all.vars(form)[1])
  names(responses) <- as.character(formulae)
  n <- nrow(data)
  fold.labels <- sample(rep(1:nfolds, length.out = n))
  mses <- matrix(NA, nrow = nfolds, ncol = length(formulae))
  colnames <- as.character(formulae)
  for (fold in 1:nfolds) {
    test.rows <- which(fold.labels == fold)
    train <- data[-test.rows, ]
    test <- data[test.rows, ]
    for (form in 1:length(formulae)) {
      current.model <- fit.function(formula = formulae[[form]], data = train, 
                                    family=family) #change here
      predictions <- predict(current.model, newdata = test, type='response') # change here
      test.responses <- test[, responses[form]]
      test.errors <- test.responses - predictions
      mses[fold, form] <- mean(test.errors^2)
    }
  }
  return(colMeans(mses))
}
```



```{r calibration-plot-function, include=FALSE}
# Code from Lecture 12
binary_calibration_plot <- function(y, model, breaks = 0:10/10, 
                                    point.color='blue', line.color='red') {
  fitted.probs = predict(model, type="response")
  ind = cut(fitted.probs, breaks)
  freq = tapply(y, ind, mean)
  ave.prob = tapply(fitted.probs, ind, mean)
  se = sqrt(ave.prob*(1-ave.prob)/table(ind))
  df = data.frame(freq, ave.prob, se)
  g <- ggplot(df, aes(ave.prob,freq)) + geom_point(color=point.color) + 
    geom_abline(slope = 1, intercept = 0,color=line.color) +
    ylab("observed frequency") + xlab("average predicted probability") +
    geom_errorbar(ymin=ave.prob-1.96*se, ymax=ave.prob+1.96*se) +
    ylim(0,1)+xlim(0,1) + 
    geom_rug(aes(x=fitted.probs,y=fitted.probs),data.frame(fitted.probs),sides='b')
  return(g)  
}

```
